Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-13 paper.tex
Updated intro section
New commands for phantom minus (handy in vectors) and minus which does not take space (to be used in matrices)
Save trees
Different numbering scheme for theorem environments
Using contour package
Black ticks on plots
Forgot to add `\rank` operator definition
Black hyperlinks

@@

\usepackage{pgfplots}
\usetikzlibrary{patterns,arrows}
\pgfplotsset{every axis/.append style={enlargelimits=0.05}}
\pgfplotsset{every axis grid/.append style={densely dotted}}

@@

% Custom commands
\newcommand{\program}[1]{{\tt #1}}
\newcommand{\La}{\mathcal{L}}
\newcommand{\neword}{\emph}
\newcommand{\pardiff}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\dpardiff}[3]{\frac{\partial^2{#1}}{\partial{#2}\partial{#3}}}
\newcommand{\abs}[1]{\left \lvert{#1}\right \rvert}
\newcommand{\norm}[1]{\left \lVert{#1}\right \rVert}
\newcommand{\set}[1]{\mathbb{#1}}
\newcommand{\mul}{\cdot}
\newcommand{\scalmult}[1]{{\left \langle #1 \right \rangle}}
\DeclareMathOperator{\extr}{extr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sp}{Sp}

\newtheorem{thm}{Теорема}[section]
\theoremstyle{remark}
\newtheorem{rem}{Замечание}[section]
\theoremstyle{definition}
\newtheorem{dfn}{Определение}[section]

@@

\usepackage[unicode,
pdftex, colorlinks, linkcolor=blue, citecolor=teal,
pdfauthor=Dmitry Dzhus]{hyperref}

@@

>>>>

\usepackage[auto]{contour}
\contourlength{1pt}

% Save trees
\usepackage[top=2.5cm, bottom=3cm, left=5cm, right=5cm]{geometry}

@@

\usepackage{pgfplots}
\usetikzlibrary{patterns,arrows}
\pgfplotsset{every axis/.append style={enlargelimits=0.05}}
\pgfplotsset{every axis grid/.append style={densely dotted}}
\pgfplotsset{every tick/.append style={black}}

@@

% Custom commands
\newcommand{\program}[1]{{\tt #1}}
\newcommand{\La}{\mathcal{L}}
\newcommand{\neword}{\emph}
\newcommand{\pardiff}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\dpardiff}[3]{\frac{\partial^2{#1}}{\partial{#2}\partial{#3}}}
\newcommand{\abs}[1]{\left \lvert{#1}\right \rvert}
\newcommand{\norm}[1]{\left \lVert{#1}\right \rVert}
\newcommand{\set}[1]{\mathbb{#1}}
\newcommand{\mul}{\cdot}
\newcommand{\scalmult}[1]{{\left \langle #1 \right \rangle}}
% Minus for matrices
\newcommand{\mm}[1]{\hspace{-7.5pt}{-{#1}}}
\newcommand{\phm}{\phantom{-}}
\DeclareMathOperator{\rank}{rg}
\DeclareMathOperator{\extr}{extr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sp}{Sp}

% Theorems, remarks and definition all share the same numbering
% sequence, which is also subordinate to sections
\newtheorem{thm}[]{Теорема}
\numberwithin{thm}{section}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Замечание}
\theoremstyle{definition}
\newtheorem{dfn}[thm]{Определение}

@@

\usepackage[unicode,
pdftex, colorlinks, linkcolor=black, citecolor=black,
pdfauthor=Dmitry Dzhus]{hyperref}

@@

Последний раздел посвящён поиск экстремальных значений целевой функции
при наличии ограничений с использованием теоремы Куна—Таккера, метода
штрафных функций и метода возможных направлений Зойтендейка.
